---
title: "Lab 01 - Hello R!"
subtitle: "Due: Tue, Jan 21 at 11:59pm"
author: ""
date: ""
output:
  html_document: default
  pdf_document: default
---

# Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(datasauRus)
```

# Exercise 1

(Type your answer to Exercise 1 here. This exercise does not require any R code). 
**Remember that in the lab we are telling you when to stage, commit, and push**!

You may knit this document to see what the template looks like. 
**When turning this document in on Gradescope, remember to knit to PDF** 
and turn in that PDF document.

# Exercise 2

(The answers for this Exercise are given for you below, but you should clean up 
some of the narrative so that it only includes what you want to turn in.)

First, let's plot the data in the dino dataset 
(we covered `ggplot2` in class on Thursday):

```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

Next calculate the correlation between `x` and `y` in this dataset 
(an explanation for this code is given in the lab document. We will cover data 
wrangling in more detail in class next week).

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

# Exercise 3

(Add code and narrative as needed. Note that the `R` chunks are labeled with 
`plot-star` and `cor-star` to provide spaces to place the code for plotting 
and calculating the correlation coefficient. To finish, clean up the narrative 
by removing these instructions)

Your narrative should go here.

```{r plot-star}
# Your code should go here! This is a comment, which should be deleted.
```

Some more narrative can go here.

```{r cor-star}
# Calculate the correlation here
```

Conclude with some more narrative, if needed.

# Exercise 4

(Add code and narrative as needed. Note that two `R` chunks are given but they 
are not labeled. Use the convention from Exercise 3 to name them appropriately.)

```{r}
# This is an unlabeled chunk
```

```{r}
# Here is another unlabeled chunk
```

# Exercise 5

(Add code and narrative as needed. Insert code chunks using the 
"insert chunk" button (a green C with a plus) and insert an `R` chunk.)
